\chapter[FESDData]{FESDData - Data Acquisition and Labelling of FESDDataset}
\label{sec:data_processing}

One of the most important aspects of machine learning is the data acquisition. In this thesis, a custom tool is developed which is capable of capturing and labelling multi-modal data. The tool is called \textbf{F}ault \textbf{E}stimator for \textbf{S}keleton \textbf{D}etection \textbf{Data} processor (FESDData). It is capable of capturing RGB-D data from multiple different RGB-D cameras as well as pose data calculated by Nuitrack. Nuitrack which was developed by 3DiVi Inc\footnote{\url{https://nuitrack.com/}}. Nuitrack was chosen as the pose estimation backbone since it provided the support of multiple different camera models as well as the ability to record the RGB-D data and pose data simultaneously.

Additionally to Nuitrack, FESDData is capable of calculating the pose information using OpenPose after the recording is done. This offers future support for other pose estimation backbones. However, OpenPose is not used in the scope of this thesis.

FESDData is designed to be easy to use, by anyone and to require minimal setup or tweaking. It allows for the rapid capture of RGB-D datasets with the pre-labelling of multiple different recordings. The parameters can be adapted to capture datasets for many different applications, e.g. action detection, where human pose estimation is used to identify an action. 

For this thesis, exercises have been derived which are designed to emulate different scenarios with different difficulties. These exercises are discussed in section \ref{sec:errors}. The labelling of errors in the data requires domain-specific knowledge and is therefore done manually. The resulting dataset, FESDDataset, is discussed in section \ref{sec:dataset}. It consists of the RGB-D data as well as the pose data and the labels for the errors for each of the joints in the pose.

In this chapter, the approach to the design of the exercises is discussed by showing the difficulties of human pose estimation. Furthermore, the data acquisition and labelling process is discussed. Finally, the features of the dataset are presented.


\input{sections/1_data_processing/0_challenging_hpe}
\input{sections/1_data_processing/1_data_acquisition}
\input{sections/1_data_processing/2_data_layout}
\input{sections/1_data_processing/3_data_labelling}
\input{sections/1_data_processing/4_dataset}